Information Distribution Depends on Language-Specific Features

### 2019-01-29 cogsci/position-info.Rmd
switchboard in cogsci draft

```{r switchboard, include=FALSE}

process_switchboard <- function() {

}

unigram_entropy <- function(tokens) {

  tokens %>%
    group_by(word_order, word) %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = sen_length)
}

tokens <- process_switchboard()

entropies <- map(2:10, ~unigram_entropy("", .x, brown_utterances)) %>%
  bind_rows()

>>>>

```{r switchboard, include=FALSE}
library(feather)

sb_tokens <- read_feather("../switchboard/switchboard.feather") %>%
  mutate(length = str_count(value, " ") + 1) %>%
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(word, value) %>%
  group_by(utterance_id) %>%
  mutate(word_order = 1:n())

unigram_entropy <- function(sen_length, tokens) {
  tokens %>%
    filter(length == sen_length) %>%
    group_by(word_order, word) %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(length = sen_length)
}

entropies <- map(2:10, ~unigram_entropy(.x, sb_tokens)) %>%
  bind_rows()
